Staged Abstract Interpreters

### 2019-09-05 paper/60_cases.tex
margin

The timestamp is essentially a finite list of expressions that tracks the $k$-most
recent calling contexts. The definition of abstract addresses @KCFAAddr@ is also
changed to include an identifier and the time when it gets allocated, meaning that
this address points to some values under such calling context. If $k$ is 0, we
obtain a monovariant analysis as demonstrated before; if $k > 0$, we obtain a
family of analyses with increasing precision. Note that when $k = 0$, the
address space is statically determined by the set of variables appeared in the
program, and we may exploit it to optimize the generated code. But when $k > 0$,
the address generation happens at the next stage, i.e., analysis time.
\begin{lstlisting}
  type AnsM[T] = RepReaderT[RepStateT[
                   RepStateT[RepSetReaderStateM[Cache, Cache, ?], Time, ?], //add Time with a RepStateT
                 Store, ?], Env, T]
  type Result = (Rep[Set[(Value, Store, Time)]], Rep[Cache])
\end{lstlisting}

>>>>

The timestamp is essentially a finite list of expressions that tracks the $k$-most
recent calling contexts. The definition of abstract addresses @KCFAAddr@ is also
changed to include an identifier and the time when it gets allocated, meaning that
this address points to some values under such calling context. If $k$ is 0, we
obtain a monovariant analysis as demonstrated before; if $k > 0$, we obtain a
family of analyses with increasing precision. Note that when $k = 0$, the
address space is statically determined by the set of variables appeared in the
program, and we may exploit it to optimize the generated code. But when $k > 0$,
the address generation happens at the next stage, i.e., analysis time.
\begin{lstlisting}
  type AnsM[T] = RepReaderT[RepStateT[RepStateT[ // add Time with a RepStateT
                  RepSetReaderStateM[Cache, Cache, ?], Time, ?], Store, ?], Env, T]
  type Result = (Rep[Set[(Value, Store, Time)]], Rep[Cache])
\end{lstlisting}
